### 2023-11-10 main.tex
''

On the occupation variable $n_{a}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we define the average density occupation of species $a$ at site $x$ as

>>>>

On the occupation variable $n_{a}^{L}$ the action is similar. \\ In the spirit of \cite{casini2022uphill} we define the average density occupation of species $a$ at site $x$ as
